\textbf{Emergency Service Location Optimization in a Multi-Zone County based on Population Distribution}

### 2013-11-16 LaTeX/paper.tex
Adding memo stub
merge
incorrect math fixed

\begin{figure}[htbp]
\label{fig:fullgraph}
\begin{center}
\includegraphics[width=3in]{6point.pdf}
\caption{Graph of zones, populations, and travel times}
\end{center}
\end{figure}

@@

Intuitively then, just by looking at the graphs, it makes the most sense that Zones 2, 5, and 3 are the most likely in which to place the ambulances in order to reach the most people in 8 minutes. Therefore, it shouldn't be surprising that when we ran the greedy algorithm for $n=3$ we got that ambulances should be placed in zones
2, 5, and 3. When we matched this up with our population coverage math, we found that this arrangement has ambulances cover all of zones 2-6 and half (25000/50000) of zone 1, accounting for a majority of the county.

\subsubsection{$n=2$}
When we ran the greedy algorithm for $n=2$ we got that ambulances should be placed in zones
2 and 5, which also intuitively follows from the graph. This arrangement has ambulances cover all of zones 2, 4-6, half      (25000/50000) of zone 1, and none of zone 3.

\subsubsection{$n=1$}
Finally, when we ran the greedy algorithm for $n=1$ we found that our ambulance should be placed in zone 2. This arrangement allows the single ambulance to cover all of zone 1-3, which represents the highest population on the map.

>>>>

\begin{figure}[htbp]
\label{fig:fullgraph}
\caption{Graph of zones, populations, and travel times}
\begin{center}
\includegraphics[width=3in]{6point.pdf}
\end{center}
\end{figure}

@@

Intuitively then, just by looking at the graphs, it makes the most sense that Zones 2, 5, and 1 are the most likely in which to place the ambulances in order to reach the most people in 8 minutes. Therefore, it shouldn't be surprising that when we ran the greedy algorithm for $n=3$ we got that ambulances should be placed in zones
2, 5, and 1. When we matched this up with our population coverage math, we found that this arrangement has ambulances cover all of zones 1-2, 4-6 and most (28333/30000) of zone 3, accounting for a majority of the county.

\subsubsection{$n=2$}
When we ran the greedy algorithm for $n=2$ we got that ambulances should be placed in zones
2 and 5, which also intuitively follows from the graph. This arrangement has ambulances cover all of zones 2, 4-6, half (25000/50000) of zone 1, and most (28333/30000) of zone 3.

\subsubsection{$n=1$}
Finally, when we ran the greedy algorithm for $n=1$ we found that our ambulance should be placed in zone 2. This arrangement allows the single ambulance to cover zone 2 and parts of 1 and 3, which represents the highest population on the map.
